% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\begin{quote}
\textbf{Aras G¨ung¨ore}\\
\emph{\textbar{} \textbar{} \textbar{} \textbar{} \textbar{}}

Education
\end{quote}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Bo˘gazi¸ci University}

\emph{B.Sc. in Electrical and Electronics Engineering; \textbf{GPA:
3.62/4.00}}

\emph{Minor Degree in Computer Science; \textbf{GPA: 3.58/4.00}}
\end{quote}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
Istanbul, Turkey \emph{Sep 2018 \textbf{--} Jun 2023 Oct 2020
\textbf{--} Jun 2023}
\end{quote}
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

\begin{quote}
\textbf{National University Admission Exam (YKS):} Ranked 75\emph{th}in
Mathematics and Science among ca. 2.3 million candidates with a test
score of 489.92/500. (Jul 2018)

Skills

\textbf{Languages:} C/C++, C\#, Java, Python, Go, JavaScript,
TypeScript, SQL, Swift, Scala, MATLAB, R

\textbf{Technologies:} Qt, Flask, Django, Node.js, React.js, MySQL,
MongoDB, Git, SVN, Docker, AWS, Kubernetes, GCP, Kafka, RabbitMQ,
OpenCV, PyTorch, TensorFlow

\textbf{Methodologies:} Agile, Scrum, OOP, Functional Programming,
DevOps, CI/CD, TDD

Experience
\end{quote}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Avikon}\\
\emph{Software Engineer}
\end{quote}\strut
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
Istanbul, Turkey\\
\emph{Dec 2023 \textbf{--} Present, Full-time}
\end{quote}\strut
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

\begin{quote}
\emph{•} Designed a Qt-based chat application utilizing TCP for
real-time communication within a client-server architecture,
demonstrating expertise in socket programming, data serialization, and
message routing.

\emph{•} Crafted message types in IDL and designed a data-centric
publish-subscribe architecture based on a flyweight design pattern to
implement OpenDDS for a radar system's command and control interface.
Utilized QoS policies to facilitate the transmission of both volatile
and persistent data across different topics.

\emph{•} Implemented a fully asynchronous AMQP-based C++ client with a
layered architecture for RabbitMQ message broker to ensure seamless
message handling among multiple topics.

\emph{•} Developed a cross-platform asynchronous program to refine UAV
detection for a GIS application. Benchmarked point-in-polygon algorithms
with a GeoJSON polygon database concurrently fetched from MongoDB.

\textbf{SemperTech} Istanbul, Turkey \emph{Software Engineer} \emph{Sep
2023 \textbf{--} Nov 2023, Full-time} \emph{•} Worked on the ``Ar¸celik
Digital Home Energy'' project in a collaborative effort with DAI-Labor
at the Technical University of Berlin under the supervision of.

\emph{•} Simulated discovery, pairing, and data exchange processes using
the EEBUS protocol suite with C\# and Go.

Migrated the framework from Go to C++ in order to ensure future
adaptability for smart home IoT devices.\emph{•} Implemented the TLS
protocol for secure data exchange using the X.509 standard and
integrated multicast DNS for seamless communication to complement the
development of SHIP and SPINE protocols.

\textbf{Max Planck Institute for Intelligent Systems}
\emph{Undergraduate Researcher}

Stuttgart, Baden\textbf{-}W¨urttemberg, Germany
\end{quote}

\emph{Jun 2022 \textbf{--} Aug 2022, Internship}

\begin{quote}
\emph{•} Engaged in collaborative research within the s and at the
Physical

Intelligence Department with Ph.D. students and on a project about 3D

printing and heat-assisted magnetic programming of soft machines under
the supervision of.

\emph{•} Optimized a C++ ROS package for real-time conversion of 3D
motion controller events to ROS messages, achieving

high-frequency and buffer-free synchronization.

\emph{•} Developed an Arduino Mega driver to activate a laser and
pressure regulator, for monitoring coil temperatures and

PID tuning to control the coil currents. Established a robust
ROS-Arduino communication network by integrating

ROSSerial and handshaking to simulate a 3D printing and magnetic
programming process with Python.

\textbf{SESTEK Speech Enabled Software Technologies} Istanbul, Turkey

\emph{AI Research and Development Intern} \emph{Jan 2022 \textbf{--} Feb
2022, Internship}

\emph{•} Developed a generative QA system with dense passage retrieval
(DPR) and retrieval-augmented generation (RAG)

techniques using the Haystack framework and PyTorch.

\emph{•} Worked on a Turkish open-domain QA system made by fine-tuning
BERTurk and XLM-Roberta models.

Tabularized exact match and F1 scores derived from DeepMind's XQuAD and
various Turkish data sets.

Awards \& Achievements

\textbf{High Honors Degree:} Awarded to Bachelor alumni who have
graduated with a GPA greater than or equal to 3.50 by Bo˘gazi¸ci
University. (Jul 2023)\\
\textbf{T ¨UB˙ITAK 2247-C Intern Researcher Scholarship:} Awarded to
students who take part in research projects carried out by the
Scientific and Technological Research Council of Turkey (T¨UB˙ITAK).
(Dec 2021 \textbf{--} Jun 2022)

\textbf{KYK Outstanding Success Scholarship:} Awarded to students who
have been ranked in the top 100 on National University Admission Exam by
Higher Education Credit and Hostels Institution (KYK). (Sep 2018
\textbf{--} Jun 2023)

\textbf{Kocaeli Science High School Valedictorian Award:} Graduated as
the highest ranked student. (Jun 2018)

Projects

\textbf{Filters and Fractals} \emph{\textbar{}}\\
\emph{•} A C project which implements a variety of image processing
operations that manipulate the size, filter, brightness, contrast,
saturation, and other properties of PPM images from scratch and
recursive fractal generation functions to model popular fractals
including Mandelbrot set, Julia set, Koch curve, Barnsley fern, and
Sierpinski triangle.

\textbf{Chess Bot} \emph{\textbar{}}\\
\emph{•} A C++ project in which you can play chess against an AI with a
specified decision tree depth that uses alpha-beta pruning algorithm to
predict the optimal move. Aside from basic moves, this mini chess engine
also implements chess rules such as castling, en passant, fifty-move
rule, threefold repetition, and pawn promotion.

\textbf{DS\&A Projects} \emph{\textbar{}}\\
\emph{•} Five Java projects that apply DS\&A concepts such as
discrete-event simulation using priority queues, Dijkstra's shortest
path algorithm, Prim's algorithm to find the minimum spanning tree,
Dinic's algorithm for maximum flow problems, and weighted job scheduling
with dynamic programming to real-world problems.
\end{quote}

\end{document}
